#4.	Fit 1, 2 and 3-nearest-neighbor classifiers to the Liver Disorders Data Set at  http://archive.ics.uci.edu/ml/datasets/Liver+Disorders for measures Euclidean and cosine.                     Last but one column is a decision attribute. Replace decision values in to 4 classes (0<=c1<5, 5<=c2<10, 10<=c3<15, 15<=c4<=20). Last column is a data split column in to training and test sets. 1 means the object is used for training. 2 means the object is used for testing. Explain the input parameters you provided for the classifier.  Compute the misclassification error on the training data and also on the test data. Annotate your program. (10M) 

```{r}
setwd("/Users/pemawangmo/Desktop/DS_Notes/DATA_MINING/Final_exam/QUESTION4")
liver_data<-read.csv("Liver_data.csv", header = FALSE, col.names = c("mcv", "alkphos", "sgpt", "sgot", "gammagt", "drinks","selector"))

str(data)
```
```{r}
#replacing the decision values into 4 classes
liver_data$selector <- as.factor(liver_data$selector)
liver_data$drinks <- cut(liver_data$drinks, breaks = c(0, 5,10,15,20), 
                     labels = c('C1', 'C2', "C3", 'C4'), right = FALSE)


```
```{r}
liver_data <- na.omit(liver_data)

```
```{r}
#selecting the train and test values 
train = subset(liver_data, liver_data$selector == 1)
str(train)

test = subset(liver_data, liver_data$selector == 2)
str(test)

```

```{r}
#train and test  variable
x_train <- subset(train, select = -c(selector, drinks))
x_test <- subset(test, select = -c(selector, drinks))
```

```{r}
#library for knn
library(class)
#train and test target variable
y_cl = train[,6, drop = TRUE]
y_test = test[,6, drop = TRUE]

#dim(train)
#dim(test)

#length(train)
#length(test)

```

```{r}
#misclassification error on training set
#when k = 1
fit1 = knn(x_train,x_train,y_cl,k=1)  
1-sum(y_train==fit1)/length(y_train)
```

```{r}
#misclassification error on training set
#when k=2
fit1 = knn(x_train,x_train,y_cl,k=2)  
1-sum(y_train==fit1)/length(y_train)   #0.0
```


```{r}
#misclassification error on training set
#when k = 3
fit1 = knn(x_train,x_train,y_cl,k=3)
1-sum(y_train==fit1)/length(y_train) #0.18
```
```{r}
#misclassification error on test set when k = 1

fit1 = knn(x_test,x_test,y_test,k=1)  
1-sum(y_test==fit1)/length(y_test)

 #0.19


```
```{r}
#K = 2

fit1 = knn(x_test,x_test,y_test,k=2)
1-sum(y_test==fit1)/length(y_test)  
```
```{r}
#k = 3

fit1 = knn(x_test,x_test,y_test,k=3)
1-sum(y_test==fit1)/length(y_test) 
```


#The input parameters provided are mcv, alkphos, sgpt, sgot, gammagt
#The output variable on which knn must be calculated is drinks.