#a) Read the data into R using data<-read.csv("twomillion.csv",header=FALSE). Note, you first need to specify your working directory using the setwd() command. Extract a simple random sample with replacement of 10,000 observations (rows). Show your R commands for doing this.

```{r}
setwd("/Users/pemawangmo/Desktop/DS_Notes/DATA_MINING/DataMiningAssignments/DM_Assignment2")
myData<-read.csv("twomillion.csv",header=FALSE)

```

```{r}
sample_data<-sample(myData[,1],10000,replace=TRUE)

```

#b) For your sample, use the functions mean(), max(), var() and quantile(,.25) to compute the mean, maximum, variance and 1st quartile respectively. Show your R code and the resulting values. 
```{r}
mean(sample_data)
```

```{r}
max(sample_data)
```
```{r}
var(sample_data)
```

```{r}
quantile(sample_data, .25)
```

#c) Compute the same quantities in part b on the entire data set and show your answers. How much do they differ from your answers in part b?
```{r}
summary(myData)
```
```{r}
mean(myData$V1)
max(myData$V1)
var(myData$V1)
quantile(myData$V1)
```

#d) Save your sample from R to a csv file using the command write.csv(). Then open this file with Excel and compute the mean, maximum, variance and 1st quartile. Provide the values and name the Excel functions you used to compute these.

```{r}
write.csv(sample_data, file = "sample_data.csv")

```

#e) Exactly what happens if you try to open the full data set with Excel?
```{r}
str(myData)
```

```{r}
#it shows all the data when i open the excel.
```

