#9) This question uses the sample of 10,000 Ohio house prices at http://www-stat.wharton.upenn.edu/~dmease/OH_house_prices.csv. Download the data set to your computer. Note that the house prices are in thousands of dollars.

#a) What is the median value? Is it larger or smaller than the mean?

```{r}
setwd("/Users/pemawangmo/Desktop/DS_Notes/DATA_MINING/DataMiningAssignments/DM_Assignment2")
ohio<-read.csv("OH_house_prices.csv", header=FALSE)
```

```{r}
median(ohio[,1])
```
```{r}
mean(ohio[,1])
```
```{r}
#median is smaller than mean

```

#b) What does your answer to part a suggest about the shape of the distribution (right-skewed or left-skewed)?
```{r}
#Since mean is greater than median, we can infer that the shape of distribution is right-skewed. 
# Yes the distribution has more weight towards the left (lower house price).
# Yes there is a long tail towards the right (higher house prices).
```
#c) How does the median change if you add 10 (thousand dollars) to all the values?
```{r}
median(ohio[,1]+10) 

```
```{r}
#The median increases by 10 (thousand dollars) to $128,000. 
```
#d) How does the median change if you multiply all the values by 2?
```{r}
median(2*ohio[,1]) 
```
```{r}
#the median doubles
```

